analysis-pilot

### 2023-07-21 code/analysis-pilot.Rmd
data cleaning 14:55

  write_csv(here(data_location, 'raw_results.csv'))
```

>>>>

# write_csv(here(data, 'rounds7.19.csv'))
```

# remove columns: numPlayers, sound, activePlayerCount, trialNum, distractor, tangramURLs, response, target, submitted, X_id, repNum, correct, targetNum, stageIds
```{r}
filtered_data <- raw_data %>% 
  select(-numPlayers) %>% 
  select(-sound) %>%  
  select(-activePlayerCount) %>% 
  select(-trialNum) %>% 
  select(-distractor) %>% 
  select(-tangramURLs) %>% 
  select(-response) %>% 
  select(-target) %>% 
  select(-submitted) %>% 
  select(-X_id) %>% 
  select(-repNum) %>% 
  select(-correct) %>% 
  select(-targetNum) %>% 
  select(-stageIds)

```

#remove NA cells in "time"
```{r}
filtered_data <- filtered_data %>% 
  drop_na(time)

View(filtered_data)
```

#relocate columns
```{r}
filtered_data <- filtered_data %>% 
  select(createdAt, everything()) %>% 
  relocate(countCorrect, .before = time)

View(filtered_data)
```

#rename columns
```{r}
colnames(filtered_data)[1] = "Date" %>% 
colnames(filtered_data)[]

View(filtered_data)
```
